\documentclass[10pt]{article}
\usepackage[margin=0.5in, top=0.4in, bottom=0.55in, footskip=0.2in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[most]{tcolorbox}
\usepackage{multicol}
\usepackage{tikz}

% Font setup — Noto Sans (modern sans-serif with full weight/style coverage)
\setmainfont{NotoSans}[
  Extension = .ttf,
  Path = /usr/share/fonts/google-noto/,
  UprightFont = *-Regular,
  BoldFont = *-Bold,
  ItalicFont = *-Italic,
  BoldItalicFont = *-BoldItalic,
]

% Colors — palette with WCAG-fixed severity colors
\definecolor{accent}{HTML}{2D3748}
\definecolor{critical}{HTML}{A82424}    % darkened from C53030 — ~5.8:1 on white
\definecolor{major}{HTML}{8B3A1A}       % darkened from C05621 — ~5.5:1 on white
\definecolor{minor}{HTML}{1E5A99}       % darkened from 2B6CB0 — ~5.2:1 on white
\definecolor{ruleline}{HTML}{A0AEC0}
\definecolor{lightbg}{HTML}{F7FAFC}
\definecolor{sectioncolor}{HTML}{1A202C}
\definecolor{stepbg}{HTML}{EDF2F7}
\definecolor{prembg}{HTML}{FFF5F0}      % warm tint for pre-mortem highlight
\definecolor{labelbg}{HTML}{E2E8F0}

% Section formatting — partial rule (35% width)
\titleformat{\section}{\fontsize{13}{15}\selectfont\bfseries\color{sectioncolor}}{}{0em}{}[{\color{ruleline}\rule{0.35\textwidth}{0.6pt}}]
\titleformat{\subsection}{\fontsize{11.5}{13}\selectfont\bfseries\color{accent}}{}{0em}{}
\titlespacing*{\section}{0pt}{12pt}{6pt}
\titlespacing*{\subsection}{0pt}{4pt}{3pt}

% List spacing
\setlist{nosep, leftmargin=1.2em}
\setlist[itemize]{label=\textcolor{accent}{\textbullet}}

% Footer with version/author, no page numbers
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[R]{\fontsize{7.5}{9}\selectfont\color{ruleline} v1 --- Aaddrick Williams}

% For measuring card heights to compute stagger
\newsavebox{\firstcardbox}
\newsavebox{\secondcardbox}
\newlength{\cardgap}
\setlength{\cardgap}{10pt}
\newlength{\staggeroffset}

% Step card box style
\newtcolorbox{stepcard}[1][]{%
  enhanced,
  boxrule=0pt,
  colback=stepbg,
  colframe=stepbg,
  arc=2pt,
  left=8pt, right=8pt, top=7pt, bottom=7pt,
  before upper={\raggedright\hyphenpenalty=10000 \exhyphenpenalty=10000},
  #1
}

% Pre-mortem card (highlighted)
\newtcolorbox{premcard}{%
  enhanced,
  boxrule=0pt,
  colback=prembg,
  colframe=prembg,
  arc=2pt,
  left=8pt, right=8pt, top=7pt, bottom=7pt,
  before upper={\raggedright\hyphenpenalty=10000 \exhyphenpenalty=10000},
  borderline west={2.5pt}{0pt}{major}
}

% Verdict pill
\newtcbox{\verdict}[1][accent]{%
  on line,
  arc=4pt,
  colback=#1!10,
  colframe=#1!40,
  boxrule=0.4pt,
  left=5pt, right=5pt, top=2pt, bottom=2pt,
  fontupper=\small\bfseries\color{#1},
  boxsep=0pt
}

\begin{document}

\begin{center}
{\fontsize{18}{20}\selectfont\bfseries\color{sectioncolor} The Helpful Contrarian}\\[4pt]
{\fontsize{10.5}{13}\selectfont\color{accent} Desk Reference --- Stress-Test Plans Before Reality Does}
\end{center}

\vspace{2pt}
\noindent
\begin{tcolorbox}[
  enhanced,
  boxrule=0pt,
  colback=lightbg,
  colframe=lightbg,
  arc=0pt,
  left=8pt, right=8pt, top=4pt, bottom=4pt,
  borderline west={3pt}{0pt}{accent}
]
\centering\itshape
When everyone agrees, assume the consensus is wrong and investigate what that world looks like.\\
Every critique must include a concrete alternative.
\end{tcolorbox}

\section{The Process}

% Measure cards to compute stagger: card2 center aligns with gap between card1 and card3
% offset = height(card1) + gap/2 - height(card2)/2
\savebox{\firstcardbox}{\begin{minipage}{0.48\textwidth}%
\begin{stepcard}
{\bfseries\color{sectioncolor}1\enspace Steel-Man First}\\[2pt]
Restate the proposal fairly \textbf{before} critiquing.
List what's genuinely strong. Critiquing without understanding is straw-manning.
\end{stepcard}
\end{minipage}}%
\savebox{\secondcardbox}{\begin{minipage}{0.48\textwidth}%
\begin{stepcard}
{\bfseries\color{sectioncolor}2\enspace Audit Assumptions}\\[2pt]
List every unstated assumption. Rate each: \textbf{likelihood wrong} vs.\ \textbf{impact if wrong}.
Focus on high-impact and uncertain. Ignore the rest.
\end{stepcard}
\end{minipage}}%
\setlength{\staggeroffset}{\dimexpr(\ht\firstcardbox + \dp\firstcardbox) + \cardgap/2 - (\ht\secondcardbox + \dp\secondcardbox)/2\relax}

\vspace{2pt}
\noindent
\begin{minipage}[t]{0.48\textwidth}
\usebox{\firstcardbox}%
\vspace{\cardgap}%
\begin{premcard}
{\bfseries\color{sectioncolor}3\enspace Pre-Mortem\enspace\textcolor{major}{\small(core)}}\\[2pt]
``It failed. Why?''
What assumption broke first? What early warning signs were missed? What cascaded?
\end{premcard}%
\vspace{\cardgap}%
\begin{stepcard}
{\bfseries\color{sectioncolor}5\enspace Second-Order Effects}\\[2pt]
What happens \textit{after} what happens?
Who else is affected that wasn't considered? What does this make harder in 6 months?
\end{stepcard}
\end{minipage}%
\hfill
\raisebox{-\staggeroffset}[0pt][0pt]{\begin{minipage}[t]{0.48\textwidth}
\usebox{\secondcardbox}%
\vspace{\cardgap}%
\begin{stepcard}
{\bfseries\color{sectioncolor}4\enspace Invert Key Decisions}\\[2pt]
What if we did the \textbf{opposite}? What if we did \textbf{nothing}?
Not every inversion is viable. The point is exposing hidden constraints.
\end{stepcard}
\end{minipage}}

\section{Findings Format}

\vspace{-1pt}
\noindent
\begin{minipage}[t]{0.52\textwidth}
\noindent
\textbf{\textcolor{critical}{Critical}} / \textbf{\textcolor{major}{Major}} / \textbf{\textcolor{minor}{Minor}} --- one-line summary

\begin{itemize}
\item \textbf{Assumption challenged} --- what belief is at risk
\item \textbf{Failure scenario} --- concrete way this breaks
\item \textbf{Recommendation} --- what to do instead
\end{itemize}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.44\textwidth}
\noindent\textbf{Verdict:}\\[4pt]
\verdict[accent]{Sound with caveats}\\[4pt]
\verdict[major]{Needs rework}\\[4pt]
\verdict[critical]{Investigate first}
\end{minipage}

\begin{multicols}{2}

\section{Anti-Patterns}

{\small\renewcommand{\arraystretch}{1.3}%
\begin{tabularx}{\linewidth}{@{}>{\bfseries\color{sectioncolor}}l X@{}}
No empty objections & Reasoning \textit{and} an alternative \\
No vague doom & Name the specific failure \\
No straw-manning & Attack what was \textit{actually} proposed \\
No reverse bias & Always disagreeing = also biased \\
Label certainty & ``will break'' vs.\ ``might break if\ldots'' \\
Target the plan & Not the person \\
\end{tabularx}
}

\columnbreak

\section{Calibrate to Stakes}

{\small\renewcommand{\arraystretch}{1.35}%
\begin{tabularx}{\linewidth}{@{}l l X@{}}
\toprule
\textbf{Stakes} & \textbf{Examples} & \textbf{Depth} \\
\midrule
Low & Reversible, minor & Blind spots only \\
Medium & Significant effort & Full assumption audit \\
High & Architecture, security & Exhaustive + pre-mortem \\
\bottomrule
\end{tabularx}
}

\end{multicols}

\vspace{4pt}
\noindent
\begin{tcolorbox}[
  enhanced,
  boxrule=0pt,
  colback=stepbg,
  colframe=stepbg,
  arc=2pt,
  left=8pt, right=8pt, top=5pt, bottom=5pt,
]
\centering\small\color{accent}\itshape
Core loop: Understand it \(\to\) Find assumptions \(\to\) Imagine it failed \(\to\) Ask ``what if the opposite?'' \(\to\) Trace ripple effects
\end{tcolorbox}

\end{document}
